Practical Optional Types for Clojure

### 2016-01-14 intro.tex
change colors, fix breaks

\begin{figure*}[t!]
  \normalsize
\begin{lstlisting}
(*typed ann pname [(U File String) -> (U nil String)] typed*)
(defmulti pname class)  ; multimethod dispatching on class of argument
(defmethod pname String [s] (*invoke pname (*interop new File s interop*) invoke*)) ; String case 
(defmethod pname File [f] (*interop .getName f interop*)) ; File case, static null check
(*invoke pname "STAINS/JELLY" invoke*) ;=> "JELLY" :- (U nil Str)
\end{lstlisting}
\caption{A simple Typed Clojure program (delimiter colors: {\color{interop}Java interoperation}, {\color{types}type annotation},
  {\color{invoke}function invocation}, {\color{red}collection literals}, {\color{mygray}miscellaneous})}
\label{fig:ex1}
\end{figure*}

>>>>

\begin{figure*}[t!]
  \normalsize
\begin{lstlisting}
(*typed ann pname [(U File String) -> (U nil String)] typed*)
(defmulti pname class)  ; multimethod dispatching on class of argument
(defmethod pname String [s] (*invoke pname (*interop new File s interop*) invoke*)) ; String case 
(defmethod pname File [f] (*interop .getName f interop*)) ; File case, static null check
(*invoke pname "STAINS/JELLY" invoke*) ;=> "JELLY" :- (U nil Str)
\end{lstlisting}
\caption{A simple Typed Clojure program (delimiter colors: {\color{interop}Java interoperation}, {\color{types}type annotation},
  {\color{invoke}function invocation (black)}, {\color{red}collection literals}, {\color{mygray}miscellaneous})}
\label{fig:ex1}
\end{figure*}
